| Base de datos de abejas ibéricas \n| Iberian bees database\n

### 2022-07-01 Manuscript/manuscript.Rmd
minor update

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
library("knitr")
#metadata <- read.csv("../Data/Metadata/attributes.csv")
library(kableExtra)

@@

kbl(d, caption = '\\textbf{Table 1}', format = 'latex', escape = F,booktabs = T, linesep = "\\addlinespace") %>% row_spec(0, bold=T)

>>>>

# Tabla 1

```{r  results='asis', echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
library("knitr")
#metadata <- read.csv("../Data/Metadata/attributes.csv")
library(kableExtra)

@@

kbl(d, format = 'latex', escape = F,booktabs = T, linesep = "\\addlinespace") %>% row_spec(0, bold=T)
